Toward Centrally Programming Distributed Control Planes

### 2016-01-22 paper/introduction.tex

Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes. We focus on BGP because it is a common and highly flexible way to implement such control planes.

>>>>

Through our system, called \sysname, we demonstrate the feasibility of centrally programming distributed control planes. We focus on BGP, a common and highly flexible way to implement distributed control planes, and show how to automatically generate router BGP configurations from a program that directly expresses network policies.
